Trademap_Data_Analysis

### 2018-12-19 sourceCode/Analysis_Data_Muh_Clustering.Rmd
Add files via upload

library(shiny)
library(tidyverse)
library(dplyr)
library(readxl)
library(leaflet)
library(reshape2)
library(ggplot2)

@@

>>>>

library(shiny)
library(tidyverse)
library(dplyr)
library(readxl)
library(leaflet)
library(reshape2)
library(ggplot2)
library(data.table)

@@

```
#K-means Clustering
```{r}
country_year<-export_Product_Group %>%
filter(Export_Value > 0) %>%
group_by(Country,year)%>%
summarise(Adet=n(), Toplam = sum(Export_Value))

#country_Adet <-data.table::dcast(country_year, Country ~ year , value.var = c("Adet","Toplam"))

country_Cluster <-dcast(country_year, Country ~ year , value.var = "Toplam") %>%
   rename(Toplam_2013 = "2013") %>%
   rename(Toplam_2014 = "2014") %>%
   rename(Toplam_2015 = "2015") %>%
   rename(Toplam_2016 = "2016") %>%
   rename(Toplam_2017 = "2017")

Normalize_country_Cluster<-country_Cluster%>%
mutate(normalized_2013 =  round((Toplam_2013  - mean(Toplam_2013))/sd(Toplam_2013 ),2)) %>%
mutate(normalized_2014 =  round((Toplam_2014  - mean(Toplam_2014))/sd(Toplam_2014 ),2)) %>%
mutate(normalized_2015 =  round((Toplam_2015  - mean(Toplam_2015))/sd(Toplam_2015 ),2)) %>%
mutate(normalized_2016 =  round((Toplam_2016  - mean(Toplam_2016))/sd(Toplam_2016 ),2)) %>%
mutate(normalized_2017 =  round((Toplam_2017  - mean(Toplam_2017))/sd(Toplam_2017 ),2)) %>%
select(Country,normalized_2013,normalized_2014,normalized_2015,normalized_2016,normalized_2017)

set.seed(20)
Cluster <- kmeans(Normalize_country_Cluster[, 2:6], 2, nstart = 20)

head(Cluster)

Normalize_country_Cluster$group<- as.factor(Cluster$cluster)

ggplot(Normalize_country_Cluster, aes(normalized_2016, normalized_2017, color = Normalize_country_Cluster$group)) + geom_point()
